Fail Faster

### 2025-03-24 paper/paper.tex

We evaluate the optimizations with a series of case studies in each
generator library, and show that the \name{} generators run faster
than their unstaged equivalents. In \camlname, they run up to $7\times$
faster, and in \scalaname, up to $13\times$ faster. Using our improved version
of \bq's \rand in \camlname, we see even greater gains---more than $12\times$---showing that
both staging and fast randomness play distinct and complementary roles in improving generator performance.
Further,
we show that generators that run
faster also find bugs faster by running our case studies in the Etna
platform~\cite{etna}, which injects bugs into a system and measures
how quickly various generators detect them. In Etna, we find bugs up 
to $3.8\times$ faster on average, and up to $13\times$ in some cases.

>>>>

We evaluate the optimizations with a series of case studies in each
generator library, and show that the \name{} generators run faster
than their unstaged equivalents. In \camlname, they run up to $7\times$
faster, and in \scalaname, up to $13\times$ faster. Using our improved version
of \bq's \rand in \camlname, we see even greater gains---more than $12\times$---showing that
both staging and fast randomness play distinct and complementary roles in improving generator performance.
Further,
we show that \camlname generators find bugs faster by running our case studies 
in the Etna platform, which uses generated values as
inputs to a pre-defined buggy system and measures how quickly different 
generators can detect the bugs.
\camlname generators find bugs up to $2.5\times$ faster on average than 
their \bq counterparts. With fast randomness, 
the average speedup rises to $3.8\times$, 
with some cases exceeding $13\times$.
